---
title: "AirBnB analysis"
author: "MK842 Team 2"
date: "1/12/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r setup2, message=FALSE, echo=FALSE}
library(bit64)
library(data.table)
library(ggplot2)
library(scales)
library(stringr)
theme_set(theme_bw())

if (0) {
  print("Creating training and test data sets from a 50/50 split of the CSV")
  air <- read.csv("listings.csv", stringsAsFactors = TRUE)

  airt <- data.table(air)

  atrain.sampled <- sample(nrow(airt), nrow(airt)/2)
  atrain <- airt[atrain.sampled]
  atest <- airt[!atrain.sampled]
  if (!setequal(union(atest$id, atrain$id), airt$id)) {
    stop("ERROR: The test and training datasets don't add up to the original dataset")
  }

  print("Saving training and test data sets")
  save(atest, file=sprintf("%s/%s", script.dir, "atest.dat"))
  save(atrain, file=sprintf("%s/%s", script.dir, "atrain.dat"))
} else {
  load(file="atrain.dat")
  load(file="atest.dat")
  if (length(intersect(atest$id, atrain$id)) > 0) {
    stop("ERROR: The test and training datasets overlap")
  }
}
```

## Training and Test datasets
```{r datasets, echo = TRUE}
summary(atrain)
summary(atest)
```


## To be deleted in Final Version: R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## To be deleted in Final Version: Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## To be deleted in Final Version: Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## To be deleted in Final Version: Slide with Plot

```{r pressure}
plot(pressure)
```

